Precise predictions for same-sign W-bosons scattering at the LHC

### 2018-02-02 Draft/input.tex
Conversion pole/OS mass
Extend and correct descriptions in Secs. 2 and 3
- updated writing rules, use Sec.~\ref{X1} for consistency reasons
- defined what s-, t-, and u-channels are
- added explanation for the VBS approximation for the reals
- no non-factorisable corrections for the O(a^6 as) virtuals
- added sentence about CKM matrix

For the mass and width of the massive particles, the following values are used:
%
\begin{alignat}{2}
                  \Mt   &=  173.21\GeV,       & \quad \quad \quad \Gt &= 0 \GeV,  \nonumber \\
                \MZOS &=  91.1876\GeV,      & \quad \quad \quad \GZOS &= 2.4952\GeV,  \nonumber \\
                \MWOS &=  80.385\GeV,       & \GWOS &= 2.085\GeV,  \nonumber \\
                M_{\rm H} &=  125.0\GeV,       &  \GH   &=  4.07 \times 10^{-3}\GeV.
\end{alignat}
%
The EW coupling is renormalised in the $G_\mu$ scheme \cite{Denner:2000bj} where
%
\begin{equation}
    G_{\mu}    = 1.16637\times 10^{-5}\GeV^{-2}.
\end{equation}
%
The numerical value of $\alpha$, corresponding to the choice of input parameters is
%
\begin{equation}
 \alpha = 7.555310522369 \times 10^{-3}.
\end{equation}
%
The complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg} is used throughout to treat unstable intermediate particles in a gauge-invariant manner.

The renormalisation and factorisation scales are set dynamically to
%
\begin{equation}
\label{eq:defscale}
 \mu_{\rm ren} = \mu_{\rm fac} = \sqrt{p_{\rm T, j_1}\, p_{\rm T, j_2}}.
\end{equation}
%
This choice of scale has been shown to provide stable NLO predictions \cite{Denner:2012dz}.

>>>>

For the mass and width of the massive particles, the following values are used:
%
\begin{alignat}{2}
                  \Mt   &=  173.21\GeV,       & \quad \quad \quad \Gt &= 0 \GeV,  \nonumber \\
                \MZOS &=  91.1876\GeV,      & \quad \quad \quad \GZOS &= 2.4952\GeV,  \nonumber \\
                \MWOS &=  80.385\GeV,       & \GWOS &= 2.085\GeV,  \nonumber \\
                M_{\rm H} &=  125.0\GeV,       &  \GH   &=  4.07 \times 10^{-3}\GeV.
\end{alignat}
%
The measured on-shell (OS) values for the masses and widths of the W and Z bosons are converted into pole values for the gauge bosons ($V=\PW,\PZ$) according to Ref.~\cite{Bardin:1988xt},
%
\begin{equation}
\begin{split}
        M_V &= \MVOS/\sqrt{1+(\GVOS/\MVOS)^2}\,, \\
   \Gamma_V &= \GVOS/\sqrt{1+(\GVOS/\MVOS)^2}.
\end{split}
\end{equation}
%
The EW coupling is renormalised in the $G_\mu$ scheme \cite{Denner:2000bj} where
%
\begin{equation}
    G_{\mu}    = 1.16637\times 10^{-5}\GeV^{-2}.
\end{equation}
%
The numerical value of $\alpha$, corresponding to the choice of input parameters is
%
\begin{equation}
 \alpha = 7.555310522369 \times 10^{-3}.
\end{equation}
The CKM-Matrix is assumed to be diagonal, meaning that we neglect mixing between different quark families.
%
The complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg} is used throughout to treat unstable intermediate particles in a gauge-invariant manner.

The renormalisation and factorisation scales are set to the dynamical scale
%
\begin{equation}
\label{eq:defscale}
 \mu_{\rm ren} = \mu_{\rm fac} = \sqrt{p_{\rm T, j_1}\, p_{\rm T, j_2}}.
\end{equation}
%
This choice of scale has been shown to provide stable NLO predictions \cite{Denner:2012dz}.

### 2018-02-02 Draft/scanNLO.tex
Extend and correct descriptions in Secs. 2 and 3
- updated writing rules, use Sec.~\ref{X1} for consistency reasons
- defined what s-, t-, and u-channels are
- added explanation for the VBS approximation for the reals
- no non-factorisable corrections for the O(a^6 as) virtuals
- added sentence about CKM matrix

We now present the inclusive study performed at NLO QCD, namely $\mathcal{O}(\alpha_s\alpha^6)$.\\
According to the results shown in sec.~\ref{subsec:LOinclusive}, the VBS approximation at LO fails in the region $m_{jj} < 200$ GeV, $|\Delta y_{jj}| < 2$; moreover, we would like to validate this approximation (and its extension to $s$--channels inclusion) at the NLO accuracy. Thus, we impose the same kinematic cuts shown in sec.~\ref{subsec:inputpar} relaxing the VBF cuts and asking for

@@

We compare three different predictions at NLO QCD: {\sc Bonsay} employs the VBS approximation ($|t|^2+|u|^2$), {\sc VBFNLO} adds the s--channel contributions ($|s|^2+|t|^2+|u|^2$) and {\sc Recola} employs full matrix--elements, adding also $t/u$ interferences, factorisable and non--factorisable QCD corrections to the leading electroweak order, as well as the EW correction to the $\mathcal{O}(\alpha_s\alpha^5)$ interference. The total cross sections within the above mentioned kinematic cuts are shown in table~\ref{tab:crosssecINCLUSIVE}

@@

In fig.~\ref{fig:mjjdyjj_1d_1} we show the distributions in the jet--jet invariant mass $m_{jj}$ and rapidity separation $\Delta y_{jj}$: at large $m_{jj}$ and large $\Delta y_{jj}$ the VBS approximation and its $s$--channel extension agree with the full calculation within few percents.

@@

Focussing on the region  $200 \GeV < m_{jj} < 500 \GeV$ and $2<|\Delta y_{jj}|<2.5$, the negative discrepancy between the $t|^2 + |u|^2$ approximation and the full computation is enhanced by up to 30 \%. The inclusion of $s$--channels cures the discrepancy in these regions; still, in the very low $m_{jj}$ a small discrepancy ($\approx$ 5 \%) becomes positive pointing out that also interferences (GP: and non--factorizable QCD corrections ?) are needed.\\
In order to investigate further the jet pair kinematics, we divide the $m_{jj},\Delta y_{jj}$ plane in 2--dimensional bins and analyze the cross--sections: in particular we compute in each bin the ratio of the approximated cross--section over the full one. In fig.~\ref{fig:ratio2d_NLO} and fig.~\ref{fig:mjjdyjj_2d_NLO} we show respectively the ratio $\sigma(|t|^2 + |u|^2)/\sigma(\textrm{full})$ and $\sigma(|s|^2+|t|^2 + |u|^2)/\sigma(\textrm{full})$.

@@

As expected, in the low invariant mass--low rapidity separation region of the jet--jet pair the VBS approximation fails badly (up to 40 \% discrepancies) and the $s$--channel inclusion lead to discrepancies of at most 5 \%. However, the positive discrepancy shown in the low $m_{jj}$ region (black curve, fig.~\ref{fig:mjjdyjj_1d_1}) can be traced back to the low $m_{jj}$, large $\Delta y_{jj}$ region of fig.~\ref{fig:mjjdyjj_2d_NLO}, where the two leading jets have soft transverse momenta, according to
\[
m_{jj}^2 = 2\,p_t^{j_1}p_t^{j_2}\,(\cosh \Delta y_{jj} - \cos \Delta\phi_{jj}) \approx 2\,p_t^{j_1}p_t^{j_2}\,\cosh \Delta y_{jj} \,\,.
\]
The same positive discrepancy of the $|s|^2 + |t|^2 + |u|^2$ approximation, in fact, can be seen in the low $p_t$ region of the leading jet in the left panel of fig.~\ref{fig:mjjdyjj_1d_2}.\\
In the large invariant mass--small rapidity separation region of fig.~\ref{fig:mjjdyjj_2d_NLO}, discrepancies at the 15 \% level are left: this can be traced back to the large $p_t$ and central rapidity region of the leading jets kinematics, shown in fig.~\ref{fig:mjjdyjj_1d_2}. For such distributions, despite the $s$--channel inclusion, the discrepancy between the approximated and full result is about 5-10 \%.\\
In the VBS signal region the VBS approximation it shows a good agreement with the full calculation.

@@

Concerning leptonic kinematcs, we show in fig.~\ref{fig:mjjdyjj_1d_3} the distributions of the lepton--lepton invariant mass and of the Zeppenfeld variable of the electron.
\begin{figure}[hbt]
\centering
{\includegraphics[scale=0.35]{figures/scanfigures/mll_nlo.pdf}}
{\includegraphics[scale=0.35]{figures/scanfigures/zel_nlo.pdf}}
\caption{NLO QCD inclusive study: distributions of the lepton--lepton invariant mass and the electron Zeppenfeld variable, obtained with full ({\sc Recola}) and approximated ({\sc VBFNLO, Bonsay}) amplitudes at order $\mathcal{O}(\alpha_s\alpha^6)$.} \label{fig:mjjdyjj_1d_3}
\end{figure}
{\bf GP: leptonic variables, comment further.}

>>>>

We now present the inclusive study performed at NLO QCD, namely $\mathcal{O}(\alpha_s\alpha^6)$.

According to the results shown in Sec.~\ref{subsec:LOinclusive}, the VBS approximation at LO fails in the region $m_{jj} < 200$ GeV, $|\Delta y_{jj}| < 2$; moreover, we would like to validate this approximation (and its extension to $s$--channels inclusion) at the NLO accuracy.
Thus, we impose the same kinematic cuts shown in sec.~\ref{subsec:inputpar} relaxing the VBS cuts and asking for

@@

We compare three different predictions at NLO QCD: {\sc Bonsay} employs the VBS approximation ($|t|^2+|u|^2$), {\sc VBFNLO} adds the s--channel contributions ($|s|^2+|t|^2+|u|^2$) and {\sc Recola} employs full matrix--elements, adding also $t/u$ interferences, factorisable and non--factorisable QCD corrections to the leading electroweak order, as well as the EW correction to the $\mathcal{O}(\alpha_s\alpha^5)$ interference.
The total cross sections within the above mentioned kinematic cuts are shown in Tab.~\ref{tab:crosssecINCLUSIVE}.

@@

In Fig.~\ref{fig:mjjdyjj_1d_1} we show the distributions in the jet--jet invariant mass $m_{jj}$ and rapidity separation $\Delta y_{jj}$: at large $m_{jj}$ and large $\Delta y_{jj}$ the VBS approximation and its $s$--channel extension agree with the full calculation within few percents.

@@

Focussing on the region  $200 \GeV < m_{jj} < 500 \GeV$ and $2<|\Delta y_{jj}|<2.5$, the negative discrepancy between the $|t|^2 + |u|^2$ approximation and the full computation is enhanced by up to 30 \%. The inclusion of $s$--channels cures the discrepancy in these regions; still, in the very low $m_{jj}$ a small discrepancy ($\approx$ 5 \%) becomes positive pointing out that also interferences (GP: and non--factorizable QCD corrections ?) are needed.\\
In order to investigate further the jet pair kinematics, we divide the $m_{jj},\Delta y_{jj}$ plane in 2--dimensional bins and analyze the cross--sections: in particular we compute in each bin the ratio of the approximated cross--section over the full one. In Fig.~\ref{fig:ratio2d_NLO} and Fig.~\ref{fig:mjjdyjj_2d_NLO} we show respectively the ratio $\sigma(|t|^2 + |u|^2)/\sigma(\textrm{full})$ and $\sigma(|s|^2+|t|^2 + |u|^2)/\sigma(\textrm{full})$.

@@

As expected, in the low invariant mass--low rapidity separation region of the jet--jet pair the VBS approximation fails badly (up to 40 \% discrepancies) and the $s$--channel inclusion lead to discrepancies of at most 5 \%. However, the positive discrepancy shown in the low $m_{jj}$ region (black curve, Fig.~\ref{fig:mjjdyjj_1d_1}) can be traced back to the low $m_{jj}$, large $\Delta y_{jj}$ region of Fig.~\ref{fig:mjjdyjj_2d_NLO}, where the two leading jets have soft transverse momenta, according to the following approximation
\begin{split}
m_{jj}^2 &= 2\,p_t^{j_1}p_t^{j_2}\,(\cosh \Delta y_{jj} - \cos \Delta\phi_{jj})
&\approx 2\,p_t^{j_1}p_t^{j_2}\,\cosh \Delta y_{jj} \,\,.
\end{split}
The same positive discrepancy of the $|s|^2 + |t|^2 + |u|^2$ approximation, in fact, can be seen in the low $p_t$ region of the leading jet in the left panel of Fig.~\ref{fig:mjjdyjj_1d_2}.\\
In the large invariant mass--small rapidity separation region of Fig.~\ref{fig:mjjdyjj_2d_NLO}, discrepancies at the 15 \% level are left: this can be traced back to the large $p_t$ and central rapidity region of the leading jets kinematics, shown in Fig.~\ref{fig:mjjdyjj_1d_2}. For such distributions, despite the $s$--channel inclusion, the discrepancy between the approximated and full result is about 5-10 \%.\\
In the VBS signal region the VBS approximation shows a good agreement with the full calculation.

@@

Concerning leptonic kinematcs, we show in Fig.~\ref{fig:mjjdyjj_1d_3} the distributions of the lepton--lepton invariant mass and of the Zeppenfeld variable of the electron.
\begin{figure}[hbt]
\centering
{\includegraphics[scale=0.35]{figures/scanfigures/mll_nlo.pdf}}
{\includegraphics[scale=0.35]{figures/scanfigures/zel_nlo.pdf}}
\caption{NLO QCD inclusive study: distributions of the lepton--lepton invariant mass and the electron Zeppenfeld variable, obtained with full ({\sc Recola}) and approximated ({\sc VBFNLO, Bonsay}) amplitudes at order $\mathcal{O}(\alpha_s\alpha^6)$.} \label{fig:mjjdyjj_1d_3}
\end{figure}
{\bf GP: leptonic variables, comment further.}
